\renewcommand\bibname{参考文献}
\begin{thebibliography}{20}

\ascii{

\bibitem{agile-principles-1st} Robert C. Martin.
  \newblock \emph{Agile Software Development, Principles, Patterns, and Practices}.

\bibitem{software-craftsman} Robert C. Martin.
  \newblock \emph{The Software Craftsman: Professionalism, Pragmatism, Pride}. 

\bibitem{clean-architecture} Robert C. Martin.
  \newblock \emph{Clean Architecture: A Craftsman's Guide to Software Structure and Design}.  

\bibitem{clean-code} Robert C. Martin. 
  \newblock \emph{Clean Code: A Handbook of Agile Software Craftsmanship}. 

\bibitem{clean-coder} Robert C. Martin.
  \newblock \emph{The Clean Coder: A Code of Conduct for Professional Programmers}. 

\bibitem{tdd-by-example} Kent Beck.
  \newblock \emph{Test Driven Development: By Example}.

\bibitem{xp-explained} Kent Beck.
  \newblock \emph{Extreme Programming Explained: Embrace Change}.

\bibitem{impl-patterns} Kent Beck.
  \newblock \emph{Implementation Patterns}.

\bibitem{refactoring} Martin Fowler, Kent Beck, John Brant, William Opdyke, Don Roberts. 
  \newblock \emph{Refactoring: Improving the Design of Existing Code}. 

\bibitem{dsl} Martin Fowler. 
  \newblock \emph{Domain-Specific Languages}. 

\bibitem{patters-arch} Martin Fowler. 
  \newblock \emph{Patterns of Enterprise Application Architecture}. 

\bibitem{microservices} Sam Newman. 
  \newblock \emph{Building Microservices: Designing Fine-Grained Systems}. 

\bibitem{gof} Erich Gamma, Richard Helm, Ralph Johnson, John Vlissides.
  \newblock \emph{Design Patterns: Elements of Reusable Object-Oriented Software}.

\bibitem{pragmatic-programmer} Andrew Hunt, David Thomas.
  \newblock \emph{The Pragmatic Programmer: From Journeyman to Master}.  

\bibitem{code-complete} Steve McConnell.
  \newblock \emph{Code Complete: A Practical Handbook of Software Construction, 2th Edition}.  

\bibitem{working-with-legacy-code} Michael Feathers.
  \newblock \emph{Working Effectively with Legacy Code}.  

\bibitem{emc} Scott Meyers.
  \newblock \emph{Effective Modern C++: 42 Specific Ways to Improve Your Use of C++11 and C++14}.   

\bibitem{eff-cpp} Scott Meyers.
  \newblock \emph{Effective C++: 55 Specific Ways to Improve Your Programs and Designs}.   

\bibitem{more-eff-cpp} Scott Meyers.
  \newblock \emph{More Effective C++: 35 New Ways to Improve Your Programs and Designs}.   

\bibitem{eff-stl} Scott Meyers.
  \newblock \emph{Effective STL: 50 Specific Ways to Improve Your Use of the Standard Template Library}.   

\bibitem{eff-java} Joshua Bloch.
  \newblock \emph{Effective Java, 3rd Edition}.   

\bibitem{prog-scala} Martin Odersky, Lex Spoon, Bill Venners.
  \newblock \emph{Programming in Scala, 3rd Edition}.   

\bibitem{prog-scala} Martin Odersky, Lex Spoon, Bill Venners.
  \newblock \emph{Programming in Scala, 3rd Edition}.   

\bibitem{tdd-c} James W. Grenning.
  \newblock \emph{Test Driven Development for Embedded C}.   


\bibitem{cpp-template} David Vandevoorde, Nicolai M. Josuttis, Douglas Gregor.
  \newblock \emph{C++ Templates: The Complete Guide}.   

\bibitem{cpp-primer} Stanley B. Lippman, Josée Lajoie, Barbara E. Moo
  \newblock \emph{C++ Primer, 5th Edition}.

\bibitem{programming-bs} Bjarne Stroustrup.
  \newblock \emph{Programming: Principles and Practice Using C++, 2th Edition}.

\bibitem{programming-cpp} Bjarne Stroustrup.
  \newblock \emph{The C++ Programming Language, 4th Edition}.

\bibitem{cpp-concurrency} Anthony Williams.
  \newblock \emph{C++ Concurrency in Action: Practical Multithreading}.

\bibitem{large-cpp-design} John Lakos.
  \newblock \emph{Large-Scale C++ Software Design}.

\bibitem{cpp-coding-std} Herb Sutter, Andrei Alexandrescu.
  \newblock \emph{C++ Coding Standards: 101 Rules, Guidelines, and Best Practices}.

\bibitem{modern-cpp-design} Andrei Alexandrescu.
  \newblock \emph{Modern C++ Design: Generic Programming and Design Patterns Applied}.

\bibitem{ddd} Eric Evans.
  \newblock \emph{Domain-Driven Design: Tackling Complexity in the Heart of Software}.

\bibitem{ddd-prac} Scott Millett, Nick Tune.
  \newblock \emph{Patterns, Principles, and Practices of Domain-Driven Design}.

\bibitem{story-mapping} Jeff Patton, Peter Economy.
  \newblock \emph{User Story Mapping: Discover the Whole Story, Build the Right Product}.


\bibitem{man-month} Frederick P. Brooks Jr.
  \newblock \emph{The Mythical Man-Month: Essays on Software Engineering}.

\bibitem{sicp} Harold Abelson, Gerald Jay Sussman.
  \newblock \emph{Structure and Interpretation of Computer Programs, 2nd Edition}.

\bibitem{c-prog} Brian W. Kernighan, Dennis M. Ritchie.
  \newblock \emph{The C Programming Language, 2nd Edition}.

\bibitem{go-prog} Alan A. A. Donovan, Brian W. Kernighan.
  \newblock \emph{The Go Programming Language}.

\bibitem{pro-git} Scott Chacon, Ben Straub.
  \newblock \emph{Pro Git, 2nd Edition}.

\bibitem{cod} David A. Patterson, John L. Hennessy.
  \newblock \emph{Computer Organization and Design: The Hardware/Software Interface, 5th Edition}.

\bibitem{intro-algo} Thomas H. Cormen, Charles E. Leiserson, Ronald L. Rivest, Clifford Stein.
  \newblock \emph{Introduction to Algorithms, 3rd Edition}.

}

\end{thebibliography}

\endinput